---
title: Rpharma workshop Demo
subtitle: Reproducible and scalable reporting using rmarkdown & heddlr
author: Farid
date: '`r Sys.Date()`'
params:
  author: ''
  input_data_file: ../dev_data/patient_risk_profiles.csv
output:
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup}
#| include: no

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(dplyr)
```


# Introduction by 


The workshop is about how to use rmarkdown and heddlr in order to build reproducible reports/dashboards 

```{r}
patient_risk_profiles <- readr::read_csv(params$input_data_file)
patient_risk_profiles <- patient_risk_profiles%>%janitor::clean_names()
# knitr::kable(patient_risk_profiles)
```


# Advanced Analysis 

## Group: age_group_20_24
```{r age_group_20_24_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_20_24 = dplyr::case_when(age_group_20_24 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_20_24)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_20_24)%>%
  echarts4r::e_pie(edema_in_prior_year)
```


The average predicted risk of migraine at the age_group_20_24 groupe
```{r age_group_20_24_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_20_24 = dplyr::case_when(age_group_20_24 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_20_24)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_20_24)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```


## Group: age_group_45_49
```{r age_group_45_49_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_45_49 = dplyr::case_when(age_group_45_49 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_45_49)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_45_49)%>%
  echarts4r::e_pie(edema_in_prior_year)
```


The average predicted risk of migraine at the age_group_45_49 groupe
```{r age_group_45_49_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_45_49 = dplyr::case_when(age_group_45_49 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_45_49)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_45_49)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```


## Group: age_group_85_89
```{r age_group_85_89_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_85_89 = dplyr::case_when(age_group_85_89 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_85_89)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_85_89)%>%
  echarts4r::e_pie(edema_in_prior_year)
```


The average predicted risk of migraine at the age_group_85_89 groupe
```{r age_group_85_89_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_85_89 = dplyr::case_when(age_group_85_89 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_85_89)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_85_89)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```


# Summary 

The results have illustrated some xxx ....


* The analysis has been done by `r params$author`