---
title: Rpharma workshop Demo
subtitle: Reproducible and scalable reporting using rmarkdown & heddlr
author: Farid
date: '`r Sys.Date()`'
params:
  author: ''
output:
  flexdashboard::flex_dashboard:
    orientation: rows
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(dplyr)
```

# Introduction by 


The workshop is about how to use rmarkdown and heddlr in order to build reproducible reports/dashboards 


```{r}
patient_risk_profiles <- readr::read_csv("dev_data/patient_risk_profiles.csv")
patient_risk_profiles <- patient_risk_profiles%>%janitor::clean_names()
# knitr::kable(patient_risk_profiles)
```

# Advanced Analysis 

## Group: age_group_10_14

```{r age_group_10_14_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_10_14 = dplyr::case_when(age_group_10_14 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_10_14)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_10_14)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_10_14 groupe

```{r age_group_10_14_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_10_14 = dplyr::case_when(age_group_10_14 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_10_14)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_10_14)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_15_19

```{r age_group_15_19_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_15_19 = dplyr::case_when(age_group_15_19 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_15_19)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_15_19)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_15_19 groupe

```{r age_group_15_19_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_15_19 = dplyr::case_when(age_group_15_19 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_15_19)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_15_19)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_20_24

```{r age_group_20_24_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_20_24 = dplyr::case_when(age_group_20_24 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_20_24)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_20_24)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_20_24 groupe

```{r age_group_20_24_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_20_24 = dplyr::case_when(age_group_20_24 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_20_24)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_20_24)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_65_69

```{r age_group_65_69_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_65_69 = dplyr::case_when(age_group_65_69 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_65_69)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_65_69)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_65_69 groupe

```{r age_group_65_69_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_65_69 = dplyr::case_when(age_group_65_69 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_65_69)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_65_69)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_40_44

```{r age_group_40_44_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_40_44 = dplyr::case_when(age_group_40_44 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_40_44)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_40_44)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_40_44 groupe

```{r age_group_40_44_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_40_44 = dplyr::case_when(age_group_40_44 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_40_44)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_40_44)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_45_49

```{r age_group_45_49_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_45_49 = dplyr::case_when(age_group_45_49 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_45_49)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_45_49)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_45_49 groupe

```{r age_group_45_49_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_45_49 = dplyr::case_when(age_group_45_49 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_45_49)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_45_49)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_55_59

```{r age_group_55_59_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_55_59 = dplyr::case_when(age_group_55_59 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_55_59)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_55_59)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_55_59 groupe

```{r age_group_55_59_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_55_59 = dplyr::case_when(age_group_55_59 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_55_59)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_55_59)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_85_89

```{r age_group_85_89_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_85_89 = dplyr::case_when(age_group_85_89 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_85_89)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_85_89)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_85_89 groupe

```{r age_group_85_89_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_85_89 = dplyr::case_when(age_group_85_89 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_85_89)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_85_89)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_75_79

```{r age_group_75_79_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_75_79 = dplyr::case_when(age_group_75_79 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_75_79)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_75_79)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_75_79 groupe

```{r age_group_75_79_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_75_79 = dplyr::case_when(age_group_75_79 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_75_79)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_75_79)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_5_9

```{r age_group_5_9_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_5_9 = dplyr::case_when(age_group_5_9 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_5_9)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_5_9)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_5_9 groupe

```{r age_group_5_9_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_5_9 = dplyr::case_when(age_group_5_9 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_5_9)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_5_9)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_25_29

```{r age_group_25_29_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_25_29 = dplyr::case_when(age_group_25_29 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_25_29)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_25_29)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_25_29 groupe

```{r age_group_25_29_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_25_29 = dplyr::case_when(age_group_25_29 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_25_29)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_25_29)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_0_4

```{r age_group_0_4_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_0_4 = dplyr::case_when(age_group_0_4 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_0_4)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_0_4)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_0_4 groupe

```{r age_group_0_4_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_0_4 = dplyr::case_when(age_group_0_4 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_0_4)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_0_4)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_70_74

```{r age_group_70_74_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_70_74 = dplyr::case_when(age_group_70_74 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_70_74)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_70_74)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_70_74 groupe

```{r age_group_70_74_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_70_74 = dplyr::case_when(age_group_70_74 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_70_74)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_70_74)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_50_54

```{r age_group_50_54_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_50_54 = dplyr::case_when(age_group_50_54 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_50_54)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_50_54)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_50_54 groupe

```{r age_group_50_54_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_50_54 = dplyr::case_when(age_group_50_54 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_50_54)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_50_54)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_60_64

```{r age_group_60_64_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_60_64 = dplyr::case_when(age_group_60_64 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_60_64)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_60_64)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_60_64 groupe

```{r age_group_60_64_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_60_64 = dplyr::case_when(age_group_60_64 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_60_64)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_60_64)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_35_39

```{r age_group_35_39_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_35_39 = dplyr::case_when(age_group_35_39 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_35_39)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_35_39)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_35_39 groupe

```{r age_group_35_39_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_35_39 = dplyr::case_when(age_group_35_39 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_35_39)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_35_39)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_30_34

```{r age_group_30_34_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_30_34 = dplyr::case_when(age_group_30_34 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_30_34)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_30_34)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_30_34 groupe

```{r age_group_30_34_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_30_34 = dplyr::case_when(age_group_30_34 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_30_34)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_30_34)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_80_84

```{r age_group_80_84_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_80_84 = dplyr::case_when(age_group_80_84 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_80_84)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_80_84)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_80_84 groupe

```{r age_group_80_84_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_80_84 = dplyr::case_when(age_group_80_84 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_80_84)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_80_84)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

## Group: age_group_90_94

```{r age_group_90_94_chunk1}
patient_risk_profiles%>%
  dplyr::mutate(age_group_90_94 = dplyr::case_when(age_group_90_94 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_90_94)%>%
  dplyr::reframe(edema_in_prior_year = dplyr::n())%>%
  echarts4r::e_chart(age_group_90_94)%>%
  echarts4r::e_pie(edema_in_prior_year)
```

The average predicted risk of migraine at the age_group_90_94 groupe

```{r age_group_90_94_chunk2}
patient_risk_profiles%>%
  dplyr::mutate(age_group_90_94 = dplyr::case_when(age_group_90_94 == 1  ~ "Yes", .default = "No"))%>%
  dplyr::group_by(age_group_90_94)%>%
  dplyr::reframe(avg_predicted_risk_of_migraine = predicted_risk_of_migraine)%>%
  echarts4r::e_chart(age_group_90_94)%>%
  echarts4r::e_bar(avg_predicted_risk_of_migraine)
```

# Summary 

The results have illustrated some xxx ....


* The analysis has been done by `r params$author`